% ------------------------------------------------------------------------
% References
\phantomsection
\addcontentsline{toc}{chapter*}{Reference}
%
\renewcommand{\bibname}{Reference}
%\putbib[BibFile_Chp3]
%
%\end{bibunit}
%
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{rmorais}
%
%

\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{alcatel}
\BIBentryALTinterwordspacing
Alcatel-Lucent (2010). ``Understanding OTN Optical Transport Network (G.709), March 9, 2010'' [Online]. Available:
  \url{http://www.cvt-dallas.org/March2010.pdf}
\BIBentrySTDinterwordspacing

\bibitem{ILP01}
L.~Gyarmati, T.~Cinkler, and G.~Sallai, ``Srlg-disjoint multi-path protection: When lp meets ILP,'' in \emph{Proc. Networks 2008 - The 13th Int. Telecommunications Network Strategy and Planning Symp}, vol. Supplement, pp. 1-10, September 2008.

\bibitem{capex}
\BIBentryALTinterwordspacing
Wikipedia ``CAPEX'' [Online]. Available:
  \url{https://pt.wikipedia.org/wiki/CAPEX}
\BIBentrySTDinterwordspacing

\bibitem{opex}
\BIBentryALTinterwordspacing
Wikipedia ``OPEX'' [Online]. Available:
  \url{https://pt.wikipedia.org/wiki/OPEX}
\BIBentrySTDinterwordspacing

\bibitem{aulas}
A.~N. Pinto, ``Design of Optical Transport Networks,'' in \emph{Aulas de redes opticas 2016-2017.}

\bibitem{ramas2010}
R. Ramaswami, K. N.~Sivarajan, and G. H. Sasaki, \emph{Optical Networks: A Practical Perspective}, Morgan Kaufmann, 2010.

\bibitem{teserui}
R.~M.~D. Morais, ``Planning and Dimensioning of Multilayer Optical Transport Networks.'' PhD thesis, Universidade de Aveiro, 2015.

\bibitem{tesevasco}
V.~R.~B.~S. Braz, ``Dimensioning and Optimization of Node Architecture in Optical Transport Networks.'' Master's thesis, Universidade de Aveiro, 2016.

\bibitem{book07}
E.~Bouillet, G.~Ellinas, J.-F. Labourdette, and R.~Ramamurthy, \emph{Path Routing in Mesh Optical Networks}, John Wiley \& Sons, 2007.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{Pavan2009}
C.~Pavan, R.~M. Morais, and A.~N. Pinto, ``Quantifying the restoration capacity in optical mesh networks,'' in \emph{Proc. Next Generation Internet Networks - NGI}, pp. 1--5, July 2009.

\bibitem{Pavan2008}
C.~Pavan, R.~M. Morais, A.~R. Correia, and A.~N. Pinto, ``Dimensioning of optical networks with incomplete information,'' in \emph{Proc. Fourth Advanced International Conference Telecommunications - AICT}, pp. 261--264, June 2008.

\bibitem{Gladisch06}
A.~Gladisch, R.-P. Braun, D.~Breuer, A.~Ehrhardt, H.-M. Foisel, M.~Jaeger,
  R.~Leppla, M.~Schneiders, S.~Vorbeck, W.~Weiershausen, and F.~Westphal,
  ``Evolution of terrestrial optical system and core network architecture,''
  \emph{Proceedings of the IEEE}, vol.~94, no.~5, pp. 869--891, June 2006.

\bibitem{babarczi11}
P.~Babarczi, ``Survivable Optical Network Design with Unambiguous Shared Risk
  Link Group Failure Localization,'' Ph.D. thesis, Budapest University of
  Technology and Economics, 2011.

\bibitem{Kerivin2005}
H.~Kerivin and A.~R. Mahjoub, ``Design of survivable networks: A survey,'' \emph{Networks}, vol.~46, pp. 1--21, August 2005.

\bibitem{morais:UA-08}
R.~M. Morais, ``Desenho Topol{\'o}gico de Redes {\'O}pticas,'' Master's thesis, University of Aveiro, Aveiro, Portugal, 2008.

\bibitem{Klopfenstein08}
O.~Klopfenstein, ``Access network dimensioning with uncertain traffic forecasts,'' in \emph{Proc International Telecommunications Network Strategy and Planning Symposium - NETWORKS}, pp. 1--52, October 2008.

\bibitem{Yang2014}
S.~Yang and F.~Kuipers, ``Traffic uncertainty models in network planning,'' \emph{IEEE Communications Magazine}, vol.~52, no.~2, pp. 172--177, February 2014.

\bibitem{Cieslik09}
D.~Cieslik, \emph{Network Design Problems}, Wiley, 2009.

\bibitem{Ramamurthy2003}
S.~Ramamurthy, L.~Sahasrabuddhe, and B.~Mukherjee, ``Survivable WDM mesh networks,'' \emph{IEEE/OSA Journal of Lightwave Technology}, vol.~21, no.~4, pp. 870--883, April 2003.

\bibitem{Jungnickel07}
D.~Jungnickel, \emph{Graphs, Networks and Algorithms}, Springer Publishing Company, 2007.

\bibitem{Garey90}
M.~R. Garey and D.~S. Johnson, \emph{Computers and Intractability: A Guide to the Theory of NP-Completeness}, W. H. Freeman \& Co., 1990.

\bibitem{Routray13}
S.~Routray, R.~M. Morais, J.~da~Rocha, and A. N.~Pinto, ``Statistical model for link lengths in optical transport networks,'' \emph{IEEE/OSA Journal of Optical Communications and
  Networking}, vol.~5, no.~7, pp. 762--773, July 2013.

\bibitem{Soni02}
\BIBentryALTinterwordspacing
S.~Soni and H.~Pirkul, ``Design of survivable networks with connectivity requirements,''  \emph{Telecommunication Systems}, vol.~20, no. 1-2, pp. 133--149, May 2002.

\bibitem{Balakrishnan04}
\BIBentryALTinterwordspacing
A.~Balakrishnan, T.~L. Magnanti, and P.~Mirchandani, ``Connectivity-splitting models for survivable network design,'' \emph{Networks}, vol.~43, no.~1, pp.
  10--27, January 2004.
\BIBentrySTDinterwordspacing

\bibitem{Balakrishnan09}
\BIBentryALTinterwordspacing
A.~Balakrishnan, P.~Mirchandani, and H.~P. Natarajan, ``Connectivity upgrade models for survivable network design,'' \emph{Operations Research}, vol.~57,
  no.~1, pp. 170--186, February 2009.

\bibitem{Soni99}
\BIBentryALTinterwordspacing
S.~Soni, R.~Gupta, and H.~Pirkul, ``Survivable network design: The state of the art,'' \emph{Information Systems Frontiers}, vol.~1, no.~3, pp. 303--315, October 1999.

\bibitem{Pavan2010}
C.~Pavan, R.~M. Morais, J. da~Rocha, and A.~N. Pinto, ``Generating realistic optical transport network topologies,'' \emph{IEEE/OSA Journal of
  Optical Communications and Networking}, vol.~2, no.~1, pp. 80--90, January 2010.

\bibitem{xpress}
\BIBentryALTinterwordspacing
Fico Xpress optimization suite (2010). [Online]. Available: \url{http://www.fico.com/en/products/fico-xpress-optimization-suite/}
\BIBentrySTDinterwordspacing

\bibitem{Huelsermann2008}
R.~Huelsermann, M.~Gunkel, C.~Meusburger, and D.~A. Schupke, ``Cost modeling and evaluation of capital expenditures in optical multilayer networks,''
  \emph{Journal of Optical Networking}, vol.~7, pp. 814--833, September 2008.
\end{thebibliography}
