
% ------------------------------------------------------------------------
\chapter{Capital expenditure}
\label{chap_capex}
The cost of a telecommunications network can be divided into capital and operational expenditures. The CAPEX is the amount of money needed to set up and install a particular network and the OPEX is the amount of money needed to run this network as well as its maintenance and operation over time \cite{capex}\cite{opex}\cite{aulas}. In this section we will only focus on CAPEX, that is the costs of installing a particular network.
The current chapter proposes and describes the optimization model used to calculate capital expenditures of the network using as a tool ILP and analytical models. These calculations are made based on the three modes of transport (opaque, transparent and translucent) with 1+1 protection and without survivability.
In the section \ref{ILP_CAPEX} it is described how the network CAPEX is calculated using ILP models and in its subsections, the calculations and constraints of the three transport modes mentioned above are identified.
In the section\ref{analytical_CAPEX} the network CAPEX is calculated using analytical models. In its subsections the calculations and constraints of the opaque and transparent modes of transport are identified.

%Section CAPEX ILP
\input{./sdf/capex/ilp_CAPEX}
%Subsection with the different transport mode
\input{./sdf/capex/ilp_opaque}
\input{./sdf/capex/ilp_transparent}
\input{./sdf/capex/ilp_translucent}

%Section CAPEX analytical
\input{./sdf/capex/analytical_CAPEX}
%Subsection with the different transport mode
\input{./sdf/capex/analytical_opaque}
\input{./sdf/capex/analytical_transparent}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% References
\phantomsection
\addcontentsline{toc}{section}{References}
%
\renewcommand{\bibname}{References}
%\bibliographystyle{IEEEtran}
%\bibliography{rmorais}
%
%
% Generated by IEEEtran.bst, version: 1.13 (2008/09/30)
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{capex}
\BIBentryALTinterwordspacing
Wikipedia ``CAPEX,'' [Online]. Available: \url{https://pt.wikipedia.org/wiki/CAPEX}
\BIBentrySTDinterwordspacing

\bibitem{opex}
\BIBentryALTinterwordspacing
Wikipedia ``OPEX,'' [Online]. Available: \url{https://pt.wikipedia.org/wiki/OPEX}
\BIBentrySTDinterwordspacing

\bibitem{aulas}
A.~N. Pinto, ``Design of Optical Transport Networks,'' \emph{Aulas de redes opticas 2016-2017.}

\bibitem{teserui}
R.~M.~D. Morais, ``Planning and Dimensioning of Multilayer Optical Transport Networks.'' PhD thesis, Universidade de Aveiro, 2015.

\bibitem{ramas2010}
R. Ramaswami, K. N.~Sivarajan, and G. H. Sasaki, \emph{Optical Networks: A Practical Perspective}, Morgan Kaufmann, 2010.

\end{thebibliography} 