
% ------------------------------------------------------------------------
\chapter{Integer linear programming}
\label{chap_ilp}
ILP models are used to design networks that describe real components and their capabilities through a set of linear equations. Despite their quality, the solutions obtained through these models, depending on the number of variables and computational resources, can take days, months or even years \cite{ILP01}.
The current chapter proposes and describes the optimization models used to calculating the capital expenditures of the network, based on the three modes of transport (opaque, transparent and translucent) without survivability and protection.
In the first section the introduction to ILP models is made.
Next, in the following sections it is proposed in detail the restrictions of the three models previously mentioned, without survivability and with protection as well as a detailed report of the obtained results for each case.
Finally in the last section all the general conclusions of these models are described.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Introduction of ILP models}

The development of an ILP model first requires the definition of the inputs, outputs and variables of the problem in a mathematical representation.
Regarding the input parameters for this work we will consider the reference network described in \ref{Reference_Network_Topology} where the network connections are in the form of an adjacency matrix called $G_{ij}$.
Also as input parameter we take into account bidirectional demand matrices $D_{odc}$ created in section \ref{Reference_Network_Traffic} for each type of client traffic with $c = [1;2;3;4;5]$ depending on the ODU, where 1 corresponds to ODU0 and 5 to ODU4.\\

The main objective is to determine the values of the decision variables, so that all linear equations are satisfied and the value of the objective function is minimized. The objective function is introduced by the keyword "minimize" and the constraint set is introduced by the expression "subject to".
To perform the implementation of the models it is necessary to use a mathematical software tool. For this we will use MATLAB which is ideal for dealing with linear programming problems and can call the LPsolve through an external interface \cite{tesevasco,opaqueILP}. In the following sections the ILP model is presented in detail for each transport mode.\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Subsection with the different transport mode
\input{./sdf/ilp/opaque_survivability/ilp_opaque_survivability}
\input{./sdf/ilp/opaque_protection/ilp_opaque_protection}
\input{./sdf/ilp/transparent_survivability/ilp_transparent_survivability}
\input{./sdf/ilp/transparent_protection/ilp_transparent_protection}
\input{./sdf/ilp/translucent_survivability/ilp_translucent_survivability}
\input{./sdf/ilp/translucent_protection/ilp_translucent_protection}
\input{./sdf/ilp/translucent_protection/ilp_translucent_protection2}
\input{./sdf/ilp/translucent_protection/ilp_translucent_protection_concl}
\input{./sdf/ilp/conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% References
\phantomsection
\addcontentsline{toc}{section}{References}
%
\renewcommand{\bibname}{References}
%\bibliographystyle{IEEEtran}
%\bibliography{rmorais}
%
%
% Generated by IEEEtran.bst, version: 1.13 (2008/09/30)
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

\bibitem{ILP01}
L.~Gyarmati, T.~Cinkler, and G.~Sallai, ``Srlg-disjoint multi-path protection: When lp meets ILP,'' in \emph{Proc. Networks 2008 - The 13th Int. Telecommunications Network Strategy and Planning Symp}, vol. Supplement, pp. 1-10, September 2008.

\bibitem{aularui}
R.~M. Morais, ``Integer Linear Programming Models for Optical Transport Networks Dimensioning,'' in \emph{Optical Networks 2016/2017}.

\bibitem{tesevasco}
V.~R.~B.~S. Braz, ``Dimensioning and Optimization of Node Architecture in Optical Transport Networks.'' Master's thesis, Universidade de Aveiro, 2016.

\bibitem{Balakrishnan09}
\BIBentryALTinterwordspacing
A.~Balakrishnan, P.~Mirchandani, and H.~P. Natarajan, ``Connectivity upgrade models for survivable network design,'' \emph{Operations Research}, vol.~57, no.~1, pp. 170--186, February 2009.

\bibitem{opaqueILP}
K. Walkowiak, M. Kucharzak, P. Kope, and A. Kasprzak, ``ILP model and algorithms for restoration of anycast flows in elastic optical networks,'' in \emph{Proc. 6th Int. Workshop Reliable Networks Design and Modeling (RNDM)}, pp. 102-108, Nov. 2014.

\bibitem{zhu_transl}
H. Zhu, H. Zang, K. Zhu, B. Mukherjee, ``A Novel Generic Graph Model for Traffic Grooming in Heterogeneous WDM Mesh Networks'', in \emph{IEEE/ACM transactions on networking}, vol. 11, no. 2, April 2003.

\bibitem{zhu_transl2}
K. Zhu, B. Mukherjee, ``Traffic Grooming in an Optical WDM Mesh Network'' in \emph{IEEE journal on selected areas in communications}, vol. 20, no. 1, January 2002.

\end{thebibliography}
